### 2016-09-26 results.tex
restructuring results.tex

\subsection{A Meta-Theorem for Privacy}
Here we prove a result that can be used to show that a large class of ``canonical''
data structures are semantically secure, with respect to leakage of the size of the set.
\jnote{It would not be too hard to generalize this to arbitrary data structures over
arbitrary objects, so long as the number of distinct queries to the PRF made by $\Rep$
depends only on ${\sf leak}$.}

@@

\todo{Privacy theorem.  Follows from Jon's general theorem.}

@@

\subsection{Domain-separated PRF-Hash}
%\heading{Construction of PRF with domain separation.}
Let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be a set-multiplicity data
structure defined on the right-side of Figure~\ref{fig:lin-and-ds}.
As with the preceding theorem, the following says (informally) that
if~$F$ is a secure PRF, then this domain-separated PRF construction is
correct against adaptive adversaries.  We note that Neidermayer et
al. in~\cite{xxx} suggest replacing the linear-PRF hash functions in
the previous construction with independently keyed PRFs as a way to
thwart their attacks.  The construction we consider now achieves the
same end, albeit via explict domain separation rather than separate
keys.

@@

\begin{theorem}\label{thm:ds-ss}
Fix $k,m,n>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.  For any set~$S$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ such that, for any adversary~$A$
\[
\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
\]
where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
The decompose $\Rep$ into $\Rep_1$ and $\Rep_2$ as follows.  On input
$S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots, s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.  On input $n,F_K(s_1),\ldots,F_K(s_{kn})$, algorithm $\Rep_2$ simply initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)]$ to 1.  It returns~$M$ as $\pubaux$.
\end{proof}

@@

\heading{Classical Bloom filter in random oracle model (ROM). }
Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.  Then $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-garbled-bf} (left side).  The following theorem proves correctness for this construction.  Again, we stress that this correctness is with respect to adaptive adversaries, aiming to find $r \geq 1$ errors (in this case, false-positives), and with public hash functions.

\todo{OW privacy proof for classic BF in the ROM}

>>>>

\subsection{Classical Bloom filter in random oracle model (ROM). }
Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.  Then $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-garbled-bf} (left side).  The following theorem proves correctness for this construction.  Again, we stress that this correctness is with respect to adaptive adversaries, aiming to find $r \geq 1$ errors (in this case, false-positives), and with public hash functions.

\todo{distributional-SS or OW privacy proof for classic BF in the ROM}

\subsection{Privacy of Secretly Keyed Canonical Data Structures}
Here we prove a result that can be used to show that a large class of ``canonical''
data structures are semantically secure, with respect to leakage of the size of the set.
\jnote{It would not be too hard to generalize this to arbitrary data structures over
arbitrary objects, so long as the number of distinct queries to the PRF made by $\Rep$
depends only on ${\sf leak}$.}

@@

The SS-privacy of the linear-PRF hash construction follows directly from~Theorem~\ref{thm:xxx}.
\todo{Privacy theorem.  Follows from Jon's general theorem.}
\begin{theorem}\label{thm:lin-privacy}
Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}. For any set~$S$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ such that, for any adversary~$A$
\[
\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
\]
where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
On input a set of distinct elements
$S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, s_3 = \langle 1,x_2\rangle, s_4=\langle 2,x_2 \rangle,\ldots,s_{2n-1}=\langle 1,x_n \rangle, s_{2n}=\langle 2,x_n \rangle$.

On input $n,F_K(s_1),F_K(s_2),\ldots,F_K(s_{2n-1}) , F_K(s_{2n})$, algorithm $\Rep_2$ initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)+j\cdot F_K(s_{i+1})\bmod m]$ to 1, for each $j \in [k]$.  It returns~$M$ as $\pubaux$.
\end{proof}

@@

\subsection{Domain-separated PRF-Hash}
%\heading{Construction of PRF with domain separation.}
Let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be a set-multiplicity data
structure defined on the right-side of Figure~\ref{fig:lin-and-ds}.
As with the preceding theorem, the following says (informally) that
if~$F$ is a secure PRF, then this domain-separated PRF construction is
correct against adaptive adversaries.  
\tsnote{Not really appropriate to say this next thing; I'll add a new section that addresses bigram DS-PRF hash.}
We note that Neidermayer et
al. in~\cite{xxx} suggest replacing the linear-PRF hash functions in
the previous construction with independently keyed PRFs as a way to
thwart their attacks.  The construction we consider now achieves the
same end, albeit via explict domain separation rather than separate
keys.

@@

\begin{theorem}\label{thm:ds-ss}
Fix $k,m,n>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.  For any set~$S$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ such that, for any adversary~$A$
\[
\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
\]
where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
On input a set of distinct elements $S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots, s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.  On input $n,F_K(s_1),\ldots,F_K(s_{kn})$, algorithm $\Rep_2$ simply initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)]$ to 1.  It returns~$M$ as $\pubaux$.
\end{proof}

@@

%%%%%%%%%%%%%%%%% Bigram DOMAIN-SEPARATED PRF %%%%%%%%%%%%%%%%%%%%

\subsection{Domain-separated PRF-Hash}
%\heading{Construction of PRF with domain separation.}
Let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be a set-multiplicity data
structure defined on the right-side of Figure~\ref{fig:lin-and-ds}.
As with the preceding theorem, the following says (informally) that
if~$F$ is a secure PRF, then this domain-separated PRF construction is
correct against adaptive adversaries.  
\tsnote{Not really appropriate to say this next thing; I'll add a new section that addresses bigram DS-PRF hash.}
We note that Neidermayer et
al. in~\cite{xxx} suggest replacing the linear-PRF hash functions in
the previous construction with independently keyed PRFs as a way to
thwart their attacks.  The construction we consider now achieves the
same end, albeit via explict domain separation rather than separate
keys.
